Rank verification for exponential families

### 2016-04-05 verifying-winner.tex
Figures added and bibTeX files included

\documentclass[11pt]{article}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{caption}
\usepackage{cleveref}
\usepackage{enumitem}
\usepackage[totalwidth=480pt, totalheight=680pt]{geometry}
\usepackage{mathrsfs}
\usepackage{tikz}

@@

Next we condition on the sufficient statistics that are multiplied to the the nuisance parameter, in other words, we consider the conditional law
$$\mathcal{L}_{\theta_1 = \theta_j}\left(\frac{X_1 - X_j}{2} \middle| X_2, \ldots, \frac{X_1 + X_j}{2}, \ldots, X_n, A_1\right),$$
or equivalently, the conditional law
$$\mathcal{L}_{\theta_1 = \theta_j}\left(X_1 \middle| X_2, \ldots, \frac{X_1 + X_j}{2}, \ldots, X_n, A_1\right),$$
which is the distribution $\text{Binomial}\left(X_1 + X_j, \frac{1}{2}\right)$ truncated by the event $A_1$. The one-sided $p$-value $p_{1j}$ is thus given as
$$\frac{\sum_{t = X_1}^{X_1 + X_j} \binom{X_1 + X_j}{t} \left(\frac{1}{2}\right)^{X_1 + X_j}}{\sum_{t = \left(X_1 + X_j\right)/2}^{X_1 + X_j} \binom{X_1 + X_j}{t} \left(\frac{1}{2}\right)^{X_1 + X_j}} = \frac{\sum_{t = X_1}^{X_1 + X_j} \binom{X_1 + X_j}{t}}{\sum_{t = \left(X_1 + X_j\right)/2}^{X_1 + X_j} \binom{X_1 + X_j}{t}},$$
and to account for the tie-breaking we adopted earlier, we
\begin{itemize}
\item multiply the first term in the numerator and the numerator by $1/m$ where $m$ is the number of observations tied for largest; otherwise,
\item multiply the first term in the denominator by $1/2$ if $X_1$ and $X_2$ has the same parity.
\end{itemize}
Noticing that if there are ties for the largest the $p$-value is $1$ and the denominator is really $1/2$ otherwise, we can write
$$p_{1j} = 1 \wedge 2 \sum_{t=X_1}^{X_1 + X_j} \binom{X_i + X_j}{t}.$$

@@

@@

>>>>

\documentclass[11pt]{article}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{caption}
\usepackage{cleveref}
\usepackage{enumitem}
\usepackage{graphicx}
\usepackage[totalwidth=480pt, totalheight=680pt]{geometry}
\usepackage{mathrsfs}
\usepackage{tikz}

@@

Next we condition on the sufficient statistics that are multiplied to the the nuisance parameter, in other words, we consider the conditional law
$$\mathcal{L}_{\pi_1 = \pi_j}\left(\frac{X_1 - X_j}{2} \middle| X_2, \ldots, \frac{X_1 + X_j}{2}, \ldots, X_n, A_1\right),$$
or equivalently, the conditional law
$$\mathcal{L}_{\pi_1 = \pi_j}\left(X_1 \middle| X_2, \ldots, \frac{X_1 + X_j}{2}, \ldots, X_n, A_1\right),$$
which is the distribution $\text{Binomial}\left(X_1 + X_j, \frac{1}{2}\right)$ truncated by the event $A_1$. The one-sided $p$-value $p_{1j}$ is thus given as
$$\frac{\sum_{t = X_1}^{X_1 + X_j} \binom{X_1 + X_j}{t} \left(\frac{1}{2}\right)^{X_1 + X_j}}{\sum_{t = \left(X_1 + X_j\right)/2}^{X_1 + X_j} \binom{X_1 + X_j}{t} \left(\frac{1}{2}\right)^{X_1 + X_j}} = \frac{\sum_{t = X_1}^{X_1 + X_j} \binom{X_1 + X_j}{t}}{\sum_{t = \left(X_1 + X_j\right)/2}^{X_1 + X_j} \binom{X_1 + X_j}{t}},$$
and to account for the tie-breaking we adopted earlier, we
\begin{itemize}
\item multiply the first term in the numerator and the numerator by $1/m$ where $m$ is the number of observations tied for largest; otherwise,
\item multiply the first term in the denominator by $1/2$ if $X_1$ and $X_2$ has the same parity.
\end{itemize}
Noticing that if there are ties for the largest the $p$-value is $1$ and the denominator is really $1/2$ otherwise, we can write
$$p_{1j} = 1 \wedge 2 \sum_{t=X_1}^{X_1 + X_j} \binom{X_i + X_j}{t}.$$

@@

It may appear quite surprising that ``verifying a winner'' as we propose in this section requires no adjustment for multiplicity, in the sense that we only need to compare the winner to the runner- up, just as we would have done if $n = 2$. After all, we know that the winner suffer’s from a winner's curse: given $X_5$ is the winner, $X_5 / N$ would overestimate $\pi_5$, and the larger $n$ is, the more severe this bias is likely to be. However, if $X_9$ is the runner-up, then $X_9 / N$ is likely biased upward nearly as much as $X_5$. Informally, we might say that $X_9$ suffer’s from a “runner-up’s curse” that is nearly as bad as the winner's curse; as a result, $X_5 - X_9$ is actually not all that biased upward. By multiplying the $p$-value by $2$, or equivalently performing a two-tailed test, takes care of what little bias there is. Indeed, performing a two-tailed test can be viewed as a sort of ``correction for multiplicity'', albeit one that we would have to make even if $n = 2$.

@@

Gupta and Nagel \cite{Gupta:1967wg} devised a rule to select a subset that includes the maximum $\pi_j$. In other words, if the selected subset is $J\left(X\right)$, they guaranteed
$$\PP\left(\argmax_j \pi_j \in J\left(X\right)\right) \ge 1 - \alpha.$$
This was achieved by finding an integer $D$, as a function on $N$ and $n$, and select by
$$J\left(X\right) = \left\{j: X_j \ge \max_k X_k - D\right\}.$$
Gupta and Nagel also provided the method to choose $D$, which we implemented.

\Cref{fig:power} gives the power curves for $\text{Multinomial}\left(N, \pi\right)$ and
$$\pi \propto \left(e^\delta, 1, \ldots, 1\right),$$
for various combinations of $N$ and $n$. The two procedure coincide if $n = 2$ as there are is actual selection.

\begin{figure}[htbp]
\begin{center}
\includegraphics[width = \textwidth]{plotMultinomialPower}
\end{center}
\caption{Power curves as a function of $\delta$. The plots in the first row all have $N = 50$ and the second row $N = 250$.}
\label{fig:power}
\end{figure}
